\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage{cmbright}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[sf]{libertine}
\usepackage{microtype}
\usepackage{paracol}
\usepackage{supertabular}
\usepackage{titlesec}
\hypersetup{colorlinks, urlcolor=black, linkcolor=black}



% Geometry
\geometry{hmargin=1.75cm, vmargin=2.5cm}
\columnratio{0.65, 0.35}
\setlength\columnsep{0.05\textwidth}
\setlength\parindent{0pt}
\setlength{\smallskipamount}{8pt plus 3pt minus 3pt}
\setlength{\medskipamount}{16pt plus 6pt minus 6pt}
\setlength{\bigskipamount}{24pt plus 8pt minus 8pt}

% Style
\pagestyle{empty}
\titleformat{\section}{\scshape\LARGE\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{\bigskipamount}{\smallskipamount}
\newcommand{\heading}[2]{\centering{\sffamily\Huge #1}\\\smallskip{\large{#2}}}
\newcommand{\entry}[4]{{{\textbf{#1}}} \hfill #3 \\ #2 \hfill #4}
\newcommand{\tableentry}[3]{\textsc{#1} & #2\expandafter\ifstrequal\expandafter{#3}{}{\\}{\\[6pt]}}

\begin{document}

\vspace*{\fill}

\begin{paracol}{2}

% Name & headline
\heading{William Campos Gambardella Ferreira}{}

\switchcolumn

% Identity card
\vspace{0.01\textheight}
\begin{supertabular}{ll}
  \footnotesize\faPhone & +351 910 502 935 \\
  \footnotesize\faEnvelope & \href{mailto:william@gambardella.eng.br}{william@gambardella.eng.br} \\
  \footnotesize\faLinkedin & \href{https://www.linkedin.com/in/william-gambardella-62b502a1}{william-gambardella-62b502a1} \\
  \footnotesize\faGithub & \href{https://github.com/gambardellawill/cv}{gambardellawill} \\
\end{supertabular}

\bigskip
\switchcolumn*


\section{education}

\entry{Universidade Federal de Uberlândia}{Bachelor’s degree in Electrical Engineering}{Uberlândia, Brazil}{2011 -- 2017}
\begin{itemize}
  \item Special studies certification in Telecommunications Engineering
\end{itemize}

\switchcolumn

\section{skills}
\begin{supertabular}{rl}
  \tableentry{\footnotesize\faCode}{Python \textperiodcentered{} Shell scripting}{}
  \tableentry{}{Git \textperiodcentered{} Linux}{}
  \tableentry{}{}{}

  \tableentry{\footnotesize\faCloud}{AWS \textperiodcentered{} Docker \textperiodcentered Kubernetes}{}
  \tableentry{}{Azure \textperiodcentered{} Terraform \textperiodcentered{} Ansible}{}
  \tableentry{}{}{}

  \tableentry{\footnotesize\faLanguage}{Portuguese \textperiodcentered{} native}{}
  \tableentry{}{English \textperiodcentered{} proficient}{}
  \tableentry{}{French \textperiodcentered{} intermediate}{}
  \tableentry{}{Spanish \textperiodcentered{} intermediate}{}
  \tableentry{}{Hebrew \textperiodcentered{} beginner}{}
\end{supertabular}

\switchcolumn*

\section{experience}

\entry{Aubay Portugal}{DevOps Consultant}{Porto, Portugal}{Jan. 2022}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item \textbf{Client:} Accenture/SAP hybris GmbH (Oct. 2023 - Mar. 2024) 
  \item Development of Groovy scripts for managing and expanding the company's CI/CD pipeline capabilities.
  \item \textbf{Technology stack:} Jenkins, Groovy, GitHub
  \item
  \item \textbf{Client:} Galp Energia S.A. (Jan. 2022 - Jul. 2023)
  \item \textbf{Key accomplishments:} Successful migration of CI/CD pipelines triggered by Jenkins to GitHub Actions for all Outsystems-based applications, writing custom workflows and glue scripts in Python to control pipeline flow.
  \item Management and maintenance of build servers and CI/CD pipelines
  \item Development of custom solutions for maintenance and monitoring Outsystems platform cloud-based
  infrastructure.
  \item \textbf{Technology stack:} Python, GitHub, Terraform, Outsystems, Shell scripting
\end{itemize}

\medskip

\entry{Zup I.T.}{Infrastructure Analyst (DevOps/SRE)}{Uberlândia, Brazil}{Jul. 2020 -- Jan. 2022}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item \textbf{Key accomplishments:} Assisted both SRE and Security teams in fulfilling the compliance requirements and addressing security vulnerabilities in our infrastructure for passing the PCI-DSS auditing procedures in 2020 and 2021.
  \item Management, maintenance and support of multi-cloud
  infrastructure for clients in the telecommunications industry
  \item Assisted the development of new products for the company as DevOps
  infrastructure analyst.
  \item Performed the role of on-call Operations analyst working on the mitigation
  of operational incidents.
  \item \textbf{Technology stack:} AWS (EC2; S3; RDS (MySQL); Apache Kafka
  (MSK); CodeArtifact; VPC; EKS), Azure (AKS;
  Vms; Virtual Network), Grafana, Zabbix, EFK
  stack, Terraform, Docker Swarm, Kubernetes, Ansible, Python, Shell scripting,
  KVM, HAProxy, OpenSSL, nginx
\end{itemize}

\medskip

\entry{Vitta}{Junior Infrastructure Analyst II (DevOps)}{Uberlândia, Brazil}{Sep. 2019 -- Jul. 2020}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item \textbf{Key accomplishments:} Implemented a data-driven business strategy for long-term reservation of the company's cloud resources by establishing a quarterly analysis of resource utilization metrics that led to a 23\% reduction in cloud costs for VMs in local currency.
  \item Management and support of AWS cloud-based infrastructure for the company’s then flagship product.
  \item Code testing, revision and troubleshooting.
  \item Management of Jenkins build orchestration servers and pipeline automation.
  \item \textbf{Technology stack:} AWS (EC2; ECS; Elastic Beanstalk; SNS; SQS; S3;
  Lambda; RDS (MySQL); CloudFormation), MongoDB, Grafana, ELK stack, Apache Kafka,
  Terraform, Docker, Bitbucket, Ansible, Kubernetes, Java, JavaScript, TypeScript,
  Jenkins, Groovy, Python, Git.
\end{itemize}

\medskip

\entry{Sankhya Gestão em Negócios}{Software Development Analyst (DevOps)}{Uberlândia, Brazil}{Mar. 2019 -- Sep. 2019}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item \textbf{Key accomplishments:} Together with the team, dropped pipeline execution time from 2 hours to just above 45 min for the company's monolithic application.
  \item Management of Jenkins build orchestration servers.
  \item Development of automation software supporting the build and
  deployment processes in order to yield better delivery times across
  the development pipeline.
  \item Workflow standardization.
  \item Synchronizing the VCS with the company’s ERP software
  \item \textbf{Technology stack:} Java, Groovy, Jenkins, SVN, Oracle, PL/SQL, MS SQL Server, in-house plug-
  ins and extensions.
\end{itemize}

\medskip

\entry{iVendas - Yandeh}{Embedded software developer}{Uberlândia, Brazil}{Oct. 2017 -- Dec. 2018}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item Performance testing and physical data analysis for benchmarking purposes, hardware and
  remote software maintenance of single-board computers.
  \item Development and maintenance of embedded business data-collection network-attached devices
  developed for the retail industry.
  \item Development of structured queries for different SQL databases and data indexation and
  integration for the Business Intelligence team.
  \item \textbf{Technology stack:} Python, ANSI C, Shell scripting, DBeaver, MySQL, PostgreSQL,
  Firebird, MS SQL Server.
\end{itemize}

\switchcolumn

\section{certifications}
\begin{supertabular}{rl}
  \tableentry{2021}{\textbf{AWS SysOps Administrator}}{}
  \tableentry{}{Associate}{}
  \tableentry{}{ID: D2QZ9TMJDB44Q3WR}{spaceafter}
  \tableentry{2020}{\textbf{Azure Fundamentals}}{}
  \tableentry{}{AZ-900}{}
  \tableentry{}{ID: H599-2834}{spaceafter}
  \tableentry{2020}{\textbf{DevOps Essentials (DEPC)}}{}
  \tableentry{}{Certiprof}{}
  \tableentry{}{ID: 43558287}{}
  \tableentry{2020}{\textbf{Scrum Foundation (SFPC)}}{}
  \tableentry{}{Certiprof}{}
  \tableentry{}{ID: TLSZZKTHKH-MMRXPSHT-RPFHHPSTPF}{}
\end{supertabular}

\bigskip

\end{paracol}

\vspace*{\fill}

\end{document}
